---
title: "Exploratory_Analysis_Info201"
author: "Bella, Lauren, Tiffany, Junna"
date: "11/15/2021"
output: html_document
---

```{r setup, include= FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r include = FALSE}
library("knitr")
source("Suicide_Table.R")
```

## Table of Aggregate Information
```{r echo=FALSE}
suicide_table
```

The reason why our group includes this table is that we want to introduce the 
summary of data we are going to use in the charts and the main focus of our group. 
Some columns in the table are related to the demographic information of people 
in the United State and Japan. They show information such as which age groups 
they are in and which sex they are. Plus, there is some information related to 
the total suicide numbers and the suicide rates from 1985 to 2015 in these two 
countries. With this table or dataset, we can successfully compare the difference 
between the suicide rate of people between the United State and Japan. 

---
title: "sex_suicide_number"
author: "Junna"
date: "11/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Chart of suicide number

```{r include=FALSE}
library("ggplot2")
source("sexchart3.R")
```

This pie chart shows the suicide number of different sexes from 5 years old to 75+ years old in the United States in 2015.

```{r echo=FALSE}
b_p1 <- ggplot(suicide_table1, aes(x="United States", y=suicide_number, fill=sex))+
  geom_bar(width = 1, stat = "identity")
b_p1
pie1 <- b_p1 + coord_polar("y", start=0)
pie1
```

This pie chart shows the suicide number of different sexes from 5 years old to 75+ years old in the Japan in 2015.

```{r echo=FALSE}
b_p2 <- ggplot(suicide_table2, aes(x="Japan", y=suicide_number, fill=sex))+
  geom_bar(width = 1, stat = "identity")
b_p2
pie2 <- b_p2 + coord_polar("y", start=0)
pie2
```
The reason that why our group made these two charts is to see the suicide number of different sexes in the United States and Japan in 2015 respectively. From these two charts, we learned that in both the United States and Japan, the suicide number of male are higher than the suicide number of female. And the suicide number in the United States are higher than the suicide number in Japan.
