---
title: "Exploratory_Analysis_Info201"
author: "Bella, Lauren, Tiffany, Junna"
date: "11/15/2021"
output: html_document
---

```{r setup, include= FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r include = FALSE}
library("knitr")
```

## Introduction
Our group chose mental health as our domain of interest because we are college
students and we care about how mental health problems can cause results such as suicide;
especially since it is so relevant in our age gorup. From the three datasets we found, we 
chose the dataset related to the suicide rates from 1985 to 2015. It can 
be used to compare the suicide numbers between different age groups and sexes 
and can even track the suicide numbers' changes over years.
Our group's main focus on this dataset is to compare the difference in suicide 
rates in two countries, the United State and Japan. In this way, we will be able 
to know which country has the highest mental health problems according to suicide rates. 


## Summary Information Paragraph
```{r include = FALSE}
source("Summary_Info.R")
```
* The percentage of women that committed suicide in 2015 in the U.S:
```{r echo=FALSE}
us_suicide_percentage_2015
```
* The percentage of women that committed suicide in Japan in 2015:
```{r echo=FALSE}
japan_suicide_percentage_2015
```
* The percentage of suicides for 1985 in the U.S.:
```{r echo=FALSE}
us_suicide_percentage_1985
```
* The percentage of suicides for 1985 in Japan:
```{r echo=FALSE}
japan_suicide_percentage_1985
```
* The percentage of men that committed suicide in 2015 in the U.S:
```{r echo=FALSE}
male_us_suicide_percentage_2015
```
* The percentage of men that committed suicide in 2015 in Japan:
```{r echo=FALSE}
male_japan_suicide_percentage_2015
```


The purpose of these values is to allow observation for the relationship between population + number of suicides for the two countries we are comparing: Japan + U.S. In order to be able to compare the suicide rates for women in these countries, the total number of suicides in both Japan + the U.S. was calculated first, then the total number of population for women was found in order to find the total percentage of women that committed suicide in 2015.
I chose women while doing this analysis due to the fact that this group is women + it seemed like something that pertained to us personally. After finding the # of suicides and population, we then divided the numbers in order to find the actual percentage of women that committed suicide in 2015 to compare those values together. I used 2015 as it was the most recent data from this data frame and seemed the most useful + relevant for the year we are in. After finding the most recent percentages, I then took the first year recorded in this data set and found the values from the earliest recorded, so we could see the comparison from earliest recorded (1985) + most recent recorded (on this data set) (2015), to see how the rate has changed.Additionally, for the last value, I calculated the percentages of males that committed suicide in both Japan + U.S. in 2015 to compare to both Japan and U.S. for 2015 and 1985.


## Table of Aggregate Information
```{r include = FALSE}
source("Suicide_Table.R")
```

```{r echo=FALSE}
kable(suicide_table, caption = "The Suicide Table")
```

The reason why our group includes this table is that we want to introduce the 
summary of data we are going to use in the charts and the main focus of our group.
And, we choose six most relevant variables to extract in this table. Some variables 
in the table are related to the demographic information of people in the United State 
and Japan. They show information such as which age groups people are in. Plus, there
are some information related to the total suicide numbers as well as the total population of 
each age group from 1985 to 2015 in these two countries. With this table or dataset, we 
can compare the difference between the suicide numbers between the United State 
and Japan by different methods and aspects and find new insights from the comparison.



## Stacked Column Chart
```{r include=FALSE}
source("Suicide_Col_Chart.R")
```

```{r echo=FALSE}
col_chart
```

The reason that why our group include this chart is that we want to compare the
suicide number in different age groups of the United State and Japan in 2015. We 
choose the stacked column chart because it can better compare the number of 
suicide in different age groups as well as in different countries.
From the chart, we find that the age group between 35-54 years get the highest
number of suicide and the second highest age group is between 55-74 years in both
countries. Based on this finding, we can suggest that the age group from 35 to 74 
years in United State and Japan get the most pressure and worries. And, the possible 
reasons behind this are the housing loan and the daily consumption of family members.



## Pie Chart
```{r include=FALSE}
source("Pie_Chart_3.R")

```

This pie chart shows the suicide number of different sexes from 5 years old to 75+ years old in the United States in 2015.

```{r echo=FALSE}
pie1
```

This pie chart shows the suicide number of different sexes from 5 years old to 75+ years old in the Japan in 2015.

```{r echo=FALSE}
pie2
```

The reason that our group made these two charts is to see the suicide number 
of different sexes in the United States and Japan in 2015 respectively. And, the
pie charts can better compare the difference between two sexes in two countries.
From these two charts, we learned that in both the United States and Japan, the 
suicide number of males is higher than the suicide number of females in 2015. As a 
result, we can suggest that in both countries, males bear more pressure than females.
However, the number of females who commit suicide in Japan is much higher than the number of 
females who commit suicide in United State, which may prove that the women in 
Japan get more pressure or worries than women in United State in 2015. 



## Line Chart
```{r include=FALSE}
source("Line_Chart_1.R")
```

```{r echo=FALSE}
male_line_chart
```


The reason our group chose to make a line chart comparing the number of suicides 
in males aged 25-34 is because suicide rates are higher in males than females, and 
we wished to target young adults. From this line chart, our group learned that the 
United States has had a higher number of suicides based on numbers alone for while. 
This wasn't a total surprise - the U.S. has a larger population than Japan. However,
something our group did find interesting was the difference in trends between the 
United States and Japan. For instance, around the year 1995, the United States sees 
a sharp decrease in suicide numbers while Japan's increases quite drastically. This 
opposite reflection continues in 2010 when U.S. suicide numbers increase while Japan's 
steadily decline. Without conducting outside research, it's hard to tell why suicide 
numbers in Japan reflect the opposite of what they are in the U.S., but it is interesting nonetheless. 
